### 2024-10-28 response/response.tex

\begin{verbatim}
p3 the recursive definition of "above" is not ideal. Maybe cut it into 
defining "directly above" and then "above" (recursively using "directly 
above")
\end{verbatim}

Done. We unrolled the recursion with the sentence ``there is a sequence~${r = r_0, \dots, r_k = s}$ of rectangles such that the bottom edge of~$r_{i-1}$ lies in the same segment as the top edge of~$r_i$ for all~$i \in [k]$''.

\begin{verbatim}
p4 when citing Figure 6 it could be mentioned (e.g. in a footnote) that 
even if for n=4 the strong rectangulotope is the permutohedron 
(combinatorially), the geometric realization is not the same (I am not 
very familiar with quotientopes but am a bit amazed by this fact, is it 
that if you remove deletable hyperplanes from the geometric realization 
of the permutohedron you would have a geometric realization of the strong 
rectangulotope with more involved vertex coordinates ?)
\end{verbatim}

We have added the following sentence: ``Note that, contrarily to what could suggest this $n = 4$ case, the strong rectangulation lattice is not isomorphic to the weak order, and the strong rectangulotope is not combinatorially equivalent to the permutahedron as soon as~$n > 4$.''

To answer your question more specifically, when $n=4$, the strong rectangulation congruence is the trivial congruence (all classes are singletons), so the quotientope is a permutahedron (but indeed not the standard one). Note that both the weak and strong rectangulotopes have has many facets as the permutahedron, and are thus obtained by moving facets, not deleting facets.

@@

\begin{verbatim}
p8 it could be mentioned when defining S(R) and T(R) that they only 
depend (?) on the weak class of R
\end{verbatim}

Done.

\begin{verbatim}
p8 Theorem 2, it is a bit confusing to have notation S with two meanings, 
maybe it could be changed for the subset notation in (ii) (and also other 
instances)
\end{verbatim}

Done. We have replaced everywhere $S \subseteq [n]$ by $X \subseteq [n]$.
